Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-01-16 R0V0.tex
Modify the paragraph about the ADMM

\mypara In the remained of this section, two network topologies are considered to illustrate the results presented in this paper. The numerical results were obtained employing the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b

@@

\mypara In all cases, the computed matrix $W$ has a block-diagonal structure as follows
\begin{equation*}
 W=\mathbin{\mathtt{diag}}\left(W_a,W_b,W_b,W_a\right)\;.
\end{equation*}
the definition of the matrices $W_a$ and $W_b$ differs, according to each case considered.

\mypara In the first one, no constraints were imposed on the matrix $Y$ (it is defined as a full matrix). More precisely, for each $k\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(k)=\{1,2,3,4\}$, for each $j\in\mathbb{N}_{[1,8]}$, $\mathbf{C}_j=\mathbb{R}^8$, and $\mathbf{X}(\mathscr{K}(k))=\{x\}$, for each $k\in\mathbb{N}_{[1,4]}$. The parser took 98  seconds to solve the MI \eqref{eq:MI formulation}. The components of the matrix $W$ and the matrix $Y$ that form a solution to \eqref{eq:MI formulation} are
\begin{equation*}
		W_a=\mathbin{\mathtt{diag}}\left(
 1.27,1.53\right),\quad W_b=\mathbin{\mathtt{diag}}\left(1.08,1.53\right)
\end{equation*}
and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:general} with elements
\begin{align*}
 \overline{Y}_{ij}(q)=&-3y_i-0.08x_iy_i\;,\\
 \underline{Y}_{ij}(q)=&-2+0.009x_i-1.2\sum_{k=1}^4 y_k^2+x_k^2\;.
\end{align*}

\begin{figure*}
\begin{equation}\label{eq:example:Y:general}
		Y(q)=\scalebox{0.75}{$\begin{bmatrix}
			\overline{Y}_{11},&\underline{Y}_{12},&-0.004y_1,&0,&-0.04y_1-0.003x_3y_1,&0.005y_1y_3,&-0.006y_1+0.001x_4y_1,&0\\
			-0.006y_2,&0,&\overline{Y}_{23},&\underline{Y}_{24},&-0.009y_2-0.001x_3y_21,&0,&-0.04y_2-0.004x_4y_2,&0.005y_2y_4\\
			-0.04y_3-0.004x_1y_3,&0,&-0.008y_3+0.001x_2y_3,&0,&\overline{Y}_{35},&\underline{Y}_{36},&-0.006y_3,&0\\
			-0.006y_4+0.001x_1y_4,&0,&-0.04-0.003x_2y_4,&0,&-0.004y_4&0,&\overline{Y}_{47},&\underline{Y}_{48}
		\end{bmatrix}$}
\end{equation}
\end{figure*}

@@

\mypara The time taken by the parser to solve the MI \eqref{eq:MI formulation}, in this case, was 3.5 seconds. The components of the matrix $W$ and the matrix $Y$ that form a solution to the \eqref{eq:MI formulation} are
\begin{equation*}
		W_a=\mathbin{\mathtt{diag}}\left(
 1.32,1.7\right)\quad\text{and}\quad W_b=\mathbin{\mathtt{diag}}\left(1.2,1.6\right)
\end{equation*}
and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:neighbor} with elements
\begin{equation*}
	Y_{ij}(q_i,\breve{q}_i)=-3.3y_i-0.09x_iy_i
\end{equation*}
for pair of indexes $(i,j)$ given as $(1,1)$, $(2,3)$, $(3,5)$ and $(4,6)$. Also, 
\begin{align*}
	Y_{12}(q_1,\breve{q}_1)=&-2.8-0.01x_1-2(y_1^2+y_2^2+x_1^2+x_2^2)\;,\\	
	Y_{24}(q_2,\breve{q}_2)=&-3-2(y_1^2+y_2^2+y_3^2+x_1^2+x_2^2+x_3^2)\;,\\	
	Y_{36}(q_3,\breve{q}_3)=&-3-2(y_2^2+y_3^2+y_4^2+x_2^2+x_3^2+x_4^2)\;,\\	
	Y_{48}(q_4,\breve{q}_4)=&-2.5-0.01x_4-1.5(y_3^2+y_4^2+x_3^2+x_4^2)\;.
\end{align*}

\begin{figure*}
\begin{equation}\label{eq:example:Y:neighbor}
	Y(q)=\scalebox{0.85}{$\begin{bmatrix}
	Y_{11}(q_1,\breve{q}_1),&Y_{12}(q_1,\breve{q}_1),&-0.001y_1,&0,&0,&0,&0,&0\\
	-0.001(y_2+x_1y_2),&0,&Y_{23}(q_2,\breve{q}_2),&Y_{24}(q_2,\breve{q}_2),&-0.003y_2,&0,&0,&0\\
	0,&0,&-0.002y_3,&0,&Y_{35}(q_3,\breve{q}_3),&Y_{36}(q_3,\breve{q}_3),&-0.002y_3,&0\\
	0,&0,&0,&0,&-0.003y_4,&0,&Y_{47}(q_4,\breve{q}_4),&Y_{48}(q_4,\breve{q}_4)
	\end{bmatrix}$}
\end{equation}
\end{figure*}

\mypara In the last case, the fully decentralized scenario has been considered. The time taken by the parser to solve the MI~\eqref{eq:MI formulation} was 2.6 seconds. In this case, $\mathscr{K}(k)=\{k\}$ and $\mathbf{X}(\mathscr{K}(k))=\{q_k\}$, where $k\in\mathbb{N}_{[1,4]}$. Moreover, 
\begin{equation*}
	\begin{array}{rl}
		\mathbf{C}_1=\mathbf{C}_2=\left\{\begin{bmatrix}1,0,0,0\end{bmatrix}^\top\right\},&\mathbf{C}_3=\mathbf{C}_4=\left\{\begin{bmatrix}0,1,0,0\end{bmatrix}^\top\right\},\\
		\mathbf{C}_5=\mathbf{C}_6=\left\{\begin{bmatrix}0,0,1,0\end{bmatrix}^\top\right\},&\mathbf{C}_7=\mathbf{C}_8=\left\{\begin{bmatrix}0,0,0,1\end{bmatrix}^\top\right\}\;.
	\end{array}
\end{equation*}
Solving the MI \eqref{eq:MI formulation} the following components the matrices $W$ and $Y$ were obtained
\begin{align*}
 W=&\mathbin{\mathtt{diag}}\left(W_a,W_b,W_b,W_a\right),\\
 Y=&\begin{bmatrix}
 	Y_{11}&Y_{12}&0&0&0&0&0&0\\
 	0&0&Y_{23}&Y_{24}&0&0&0&0\\
 	0&0&0&0&Y_{35}&Y_{36}&0&0\\
 	0&0&0&0&0&0&Y_{47}&Y_{48}
 \end{bmatrix}
\end{align*}
where
\begin{equation*}
		W_a=\mathbin{\mathtt{diag}}\left(
 1.4,1.6\right),\quad W_b=\mathbin{\mathtt{diag}}\left(1.2,1.6\right)
\end{equation*}
and
\begin{align*}
 Y_{11}(q_i)=Y_{47}(q_i)=&\ -3.1y_i+0.06x_iy_i\;,\\
 Y_{12}(q_i)=Y_{48}(q_i)=&\ -3.6-0.02x_i-2.3y_i^2-2.4x_i^2\;,\\
 Y_{23}(q_i)=Y_{35}(q_i)=&\ -3.1y_i\;,\\
 Y_{24}(q_i)=Y_{26}(q_i)=&\ -3.8-2.1y_i^2-2.2x_i^2\;.
\end{align*}

@@

\mypara Using ADMM to solve the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual},  the solver took 23 seconds to compute the matrix $W$ for system~\eqref{eq:example} with four agents lead to the

>>>>

\mypara In the remaining of this section, two network topologies are considered to illustrate the results presented in this paper. The numerical results were obtained employing the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b

@@

\mypara In the first one, no constraints were imposed on the matrix $Y$ (it is defined as a full matrix). More precisely, for each $k\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(k)=\{1,2,3,4\}$, for each $j\in\mathbb{N}_{[1,8]}$, $\mathbf{C}_j=\mathbb{R}^8$, and $\mathbf{X}(\mathscr{K}(k))=\{x\}$, for each $k\in\mathbb{N}_{[1,4]}$. The parser took 98  seconds to solve the MI \eqref{eq:MI formulation}. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(1,1,2,1,2,1,1,1)
\end{equation*}
and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:general} with elements
\begin{align*}
 \overline{Y}_{ij}(q)=&-2y_i\;,\\
 \underline{Y}_{ij}(q)=&-2-2\sum_{k=1}^4 y_k^2+x_k^2\;.
\end{align*}

\begin{figure*}
\begin{equation}\label{eq:example:Y:general}
		Y(q)=\begin{bmatrix}
			\overline{Y}_{11}(q),&\underline{Y}_{12}(q),&0,&0,&-0.03y_1,&0,&0&0\\
			0,&0,&\overline{Y}_{23}(q),&\underline{Y}_{24}(q),&0,&0,&-0.04y_2,&0\\
			-0.04y_3,&0,&0,&0,&\overline{Y}_{35}(q),&\underline{Y}_{36}(q),&0,&0\\
			0,&0,&-0.03y_4,&0,&0,&0,&\overline{Y}_{47}(q),&\underline{Y}_{48}(q)
		\end{bmatrix}
\end{equation}
\end{figure*}

@@

\mypara The time taken by the parser to solve the MI \eqref{eq:MI formulation}, in this case, was 3.5 seconds. The matrix $W$ is given by
\begin{equation*}
		W=\mathbin{\mathtt{diag}}(2,1,1,1,1,1,2,1)
\end{equation*}
and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:neighbor} with elements
\begin{align*}
	Y_{12}(q_1,\breve{q}_1)=&-2.5(1+\sum_{j=1}^2x_j^2+y_j^2)\;,\\	
	Y_{24}(q_2,\breve{q}_2)=&-2.3(1+\sum_{j=1}^3x_j^2+y_j^2)\;,\\	
	Y_{36}(q_3,\breve{q}_3)=&-2.2(1+\sum_{j=2}^4x_j^2+y_j^2)\;,\\	
	Y_{48}(q_4,\breve{q}_4)=&-1.7(1+\sum_{j=3}^4x_j^2+y_j^2)\;.\\	
\end{align*}

\begin{figure*}
\begin{equation}\label{eq:example:Y:neighbor}
	Y(q)=\begin{bmatrix}
	-1.8y_1,&Y_{12}(q_1,\breve{q}_1),&0,&0,&0,&0,&0,&0\\
	0,&0,&-2y_2,&Y_{24}(q_2,\breve{q}_2),&0,&0,&0,&0\\
	0,&0,&0,&0,&-2y_3,&Y_{36}(q_3,\breve{q}_3),&0,&0\\
	0,&0,&0,&0,&0,&0,&-2y_4,&Y_{48}(q_4,\breve{q}_4)
	\end{bmatrix}
\end{equation}
\end{figure*}

\mypara In the last case, the fully decentralized scenario has been considered. The time taken by the parser to solve the MI~\eqref{eq:MI formulation} was 2.6 seconds. In this case, $\mathscr{K}(k)=\{k\}$ and $\mathbf{X}(\mathscr{K}(k))=\{q_k\}$, where $k\in\mathbb{N}_{[1,4]}$. Moreover, 
\begin{equation*}
	\begin{array}{rl}
		\mathbf{C}_1=\mathbf{C}_2=\left\{\begin{bmatrix}1,0,0,0\end{bmatrix}^\top\right\},&\mathbf{C}_3=\mathbf{C}_4=\left\{\begin{bmatrix}0,1,0,0\end{bmatrix}^\top\right\},\\
		\mathbf{C}_5=\mathbf{C}_6=\left\{\begin{bmatrix}0,0,1,0\end{bmatrix}^\top\right\},&\mathbf{C}_7=\mathbf{C}_8=\left\{\begin{bmatrix}0,0,0,1\end{bmatrix}^\top\right\}\;.
	\end{array}
\end{equation*}
Solving the MI \eqref{eq:MI formulation} the following matrices $W$ and $Y$ were obtained
\begin{align*}
 W=&\mathbin{\mathtt{diag}}\left(2,1,1,1,1,1,1,1\right),\\
 Y(q)=&\begin{bmatrix}
 	\overline{Y}(q_1)&0&0&0\\
 	0&\overline{Y}(q_2)&0&0\\
 	0&0&\overline{Y}(q_3)&0\\
 	0&0&0&\overline{Y}(q_4)
 \end{bmatrix}
\end{align*}
where
\begin{align*}
 \overline{Y}(q_i)=-\begin{bmatrix}2y_i,3+2(x_i^2+y_i^2)\end{bmatrix}
\end{align*}

@@

\mypara Note that the ADMM cannot be employed to compute $W$ using the MI~\eqref{eq:Artstein-Sontag:inequality:dual}, in this case. This follows from the fact that $\ker(B)\equiv0$.
